### 2022-07-22 main/chapter_2ljets.tex
begin sample comparisons

% Thanks to Jon Long, Alessia Murrone
This section only covers some of the the most peculiar or important aspects
of our signal and background modelling, and does not specify most exact
details.
Full details are publically available through the $\twoljets$
HEPData~\cite{hepdata.116034, Maguire_2017} archive our json-serialized pyhf
workspaces~\cite{cranmer2012histfactory, heinrich2021pyhf}.
\emph{Thanks to Jon~Long for collabouration in preparing this HEPData archive,
and to Alessia~Murrone for invaluable feedback on, and validation of, its
drafts.}

@@

\subsection{Sample comparisons}
\label{sec:2ljets_sample_comparisons}
Figure~\ref{fig:2ljets_low_sr_or_cr_region_alt}
Figure~\ref{fig:2ljets_low_crz_pre_post}
Figure~\ref{fig:2ljets_vrlow_alt}
Figure~\ref{fig:2ljets_low_vrlow_pre_post}

Table~\ref{tab:2ljets_zjets_alt}

\begin{table}[tp]
\centering
\begin{tabular}{lcc}
& Central
& Relative variations
\\[0.5em]
CR-DY
& $59.64$
& $1-0.1+0.1$
\\[0.2em]
\underline{CR-Z}
& $101.95$
& $1+0.2-0.2$
\\[0.2em]
CR-tt
& $38.07$
& $1+0.5-0.5$
\\[0.2em]
CR-VZ
& $5.03$
& $1+1.3-1.0$
\\[0.5em]
VR-Low
& $24.19$
& $1-0.3+0.3$
\\[0.2em]
VR-Low-2
& $17.05$
& $1+0.2-0.2$
\\[0.5em]
\underline{SR-Low-a}
& $14.30$
& $1-0.2+0.2$
\\[0.2em]
\underline{SR-Low-b}
& $4.17$
& $1-0.3+0.3$
\\[0.2em]
SR-Low-2
& $1.51$
& $1+1.5-1.0$
\\[0.2em]
\end{tabular}
\caption[%
Alternative $\zjets$ variations in selected regions
]{%
Alternative $\zjets$ variations in selected regions.
The `Central' column shows the central $\zjets$ yield from the main sample.
The other column shows the relative scale factors applied to this central yield
for up and down variations.
These are evaluated from the central and alternative samples as described in
the text.
Note how up and down variations can move in different directions.
}
\label{tab:2ljets_zjets_alt}
\end{table}

>>>>

This section only covers some of the the most peculiar or important aspects
of our signal and background modelling, and does not specify most exact
details.
Full details are publically available through the $\twoljets$
HEPData~\cite{hepdata.116034, Maguire_2017} archive our json-serialized pyhf
workspaces~\cite{cranmer2012histfactory, heinrich2021pyhf}.
\emph{Thanks to Jon~Long for collabouration in preparing this HEPData archive,
and to Alessia~Murrone for invaluable feedback on, and validation of, its
drafts.}

@@

\subsection{Sample comparisons}
\label{sec:2ljets_sample_comparisons}
The Standard Model is a distillation of past data, and all of our simulations
of it have been tuned to those data, in both their treatment of fundamental
physics and of experimental hardware.%
\footnote{%
Amusingly, tuning to data specific to each experiment means that each
experiment can simulate different fundamental physics~\cite{
herwig2000parameter,
Altarelli:473529
}, not only different detector responses.
All Standard Models are not the same.
}
Each tune yields a point estimate that does not incorporate remaining
uncertainties, so those uncertainties must be quantified by other means.
Some uncertainties are included as weights, particularly those for
uncertainties in the
PDFs (parton distribution functions) and phyiscal scales
(renormalization and factorization scales, $\mu_R$ and $\mu_F$).
Our inclusion of these weighty variations through standard prescriptions is
described in Section~\ref{sec:2ljets_theory_variations}.

To include other uncertainties that are not described by weights,
the standard approach is to compare the results of different simulation
algorithms, and we implement this for our major backgrounds $\zjets$, $\ttbar$,
and, to some extent diboson.
Each generator (simulation algorithm), or component thereof, uses different
approximate methods in its simulations, so the variations between simulations
indicate something about a reasonable uncertainty scale.

Clearly, it could happen that two algorithms agree in their tune despite
neither being confident --- as an illustration, imagine a wide error bar and
two post-fit results right in its centre.
This effect would yield an underestimated uncertainty, so does not invalidate
the comparison approach.
On the contrary, it highlights that it is a bare minimum and that larger
uncertainties may well be reasonable given our imprecise constraints on the
Standard Model.

Figure~\ref{fig:2ljets_low_sr_or_cr_region_alt}
Figure~\ref{fig:2ljets_low_crz_pre_post}
Figure~\ref{fig:2ljets_vrlow_alt}
Figure~\ref{fig:2ljets_low_vrlow_pre_post}

For implementations in the HistFactory model, these variations reduce to
the relative scale factors presented in Table~\ref{tab:2ljets_zjets_alt}.
Note that up and down variations of the sample comparison parameter do not
mean up and down variations of bin yields, but to the coupled variations
in directions given by the signs of the relative variations given in the
various regions.

\begin{table}[tp]
\centering
\begin{tabular}{lcc}
& Central
& Relative variations
\\[0.5em]
CR-DY
& $59.64$
& $1-0.1+0.1$
\\[0.2em]
\underline{CR-Z}
& $101.95$
& $1+0.2-0.2$
\\[0.2em]
CR-tt
& $38.07$
& $1+0.5-0.5$
\\[0.2em]
CR-VZ
& $5.03$
& $1+1.3-1.0$
\\[0.5em]
VR-Low
& $24.19$
& $1-0.3+0.3$
\\[0.2em]
VR-Low-2
& $17.05$
& $1+0.2-0.2$
\\[0.5em]
\underline{SR-Low-a}
& $14.30$
& $1-0.2+0.2$
\\[0.2em]
\underline{SR-Low-b}
& $4.17$
& $1-0.3+0.3$
\\[0.2em]
SR-Low-2
& $1.51$
& $1+1.5-1.0$
\\[0.2em]
\end{tabular}
\caption[%
Alternative $\zjets$ variations in selected regions
]{%
Alternative $\zjets$ variations in selected regions that have significant
$\zjets$ contributions.
In other regions the $\zjets$ sample and its variations are negligible.
The `Central' column shows the central $\zjets$ yield from the main sample.
The other column shows the relative scale factors applied to this central yield
for up and down variations.
These are evaluated from the central and alternative samples as described in
the text.
Note how up and down variations can move in different directions, and these
different movements are coupled in the background model.
}
\label{tab:2ljets_zjets_alt}
\end{table}
